MSDS6372Project1

### 2021-01-21 MSDS6372Project1.Rmd
update to Performance and High-Performance issue

#Market.Category: Crossover,Diesel,Exotic,Luxury,High-Performance,Factory Tuner,Performance,Flex Fuel,Hatchback,Hybrid,N/A
marketCat = c("Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
marketCat = data.frame(marketCat)
str = "Hatchback,Factory Tuner,High-Performance,N/A";
grepl(marketCat[11,1],str)

@@

str(CarData)
# Use For loop to fill in Yes/No to each Market Category column
for(j in 1:dim(marketCat)[1]){
  CarData[marketCat[j,1]] = ifelse(grepl(marketCat[j,1],CarData$Market.Category),"Yes","No")
}

# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style","Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Market.Category)

>>>>

#Market.Category: Crossover,Diesel,Exotic,Luxury,High-Performance,Factory Tuner,Performance,Flex Fuel,Hatchback,Hybrid,N/A (Note: Performance column will be handled individually becuase of presence of High-Performance)
marketCat = c("Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Flex Fuel","Hatchback","Hybrid","N/A")
marketCat = data.frame(marketCat)
str = "Hatchback,Factory Tuner,High-Performance,N/A";
grepl(marketCat[11,1],str)

@@

str(CarData)
# Use For loop to fill in Yes/No to each Market Category column
for(j in 1:dim(marketCat)[1]){
  CarData[marketCat[j,1]] = ifelse(grepl(marketCat[j,1],CarData$Market.Category),"Yes","No")
}
# Performance is being handled individually...
CarData$Performance = ifelse(grepl("Performance",CarData$Market.Category)&(!grepl("High-Performance",CarData$Market.Category)),"Yes","No")

CarData %>% select(Market.Category,Performance,'High-Performance','Flex Fuel')
# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style","Crossover","Diesel","Exotic","Luxury","High-Performance","Factory Tuner","Performance","Flex Fuel","Hatchback","Hybrid","N/A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Market.Category)
